Online {\IterComp}

### 2017-09-15 prof.tex
minor changes

Our relaxation strategy operates on selection of probes and weights as decided by the optimal algorithm. Removing low weight probes is
easy, but we need a way to guarantee that the error in our work estimation will not grow too big.
To this end, we first propose a more conservative approach that
calculates induced error from removing a probe by considering
    the worst case of any execution path through the program,
and then we propose a more aggressive approach that
    computes induced error based on the relative change of the work measurement that removing a probe would make to the total amount work for the whole program.
We discuss each one of them in detail.

@@

For a program with a set of probes $\{P_0, P_1, \ldots, P_k\}$, similar to the \WCRelaxLower relaxation,
we model the \WPRelaxLower relaxation as the following 0-1 Knapsack problem:
\begin{gather*}
\textrm{max.}\quad\sum_{i=0}^{k} f(P_i)x_i,\quad
\textrm{s.t.}\quad\sum_{i=0}^{k} \varepsilon(P_i)x_i \leq M \\
x_i\in\{0,1\}, i\in\{0,\ldots,k\}
\end{gather*}
where $f(P_i)$ is the execution frequency of the instrumented basic block $P_i$, $x_i$ denotes the probes selected for removal, $M$ is the
error threshold, and $\varepsilon(P_i)$ is the error of removing probe $P_i$ relative to the total work.

>>>>

Our relaxation strategy operates on selection of probes and weights as decided by the optimal algorithm. Removing low weight probes is
easy, but we need a way to guarantee that the error in our work estimation will not grow too large.
To this end, we first propose a more conservative approach that
calculates induced error from removing a probe by considering
    the worst case of any execution path through the program,
and then we propose a more aggressive approach that
    computes induced error based on the relative change of the work measurement that removing a probe would make to the total amount work for the whole program.
We discuss each one of them in detail.

@@

For a program with a set of probes $\{P_0, P_1, \ldots, P_k\}$,
we also model the \WPRelaxLower relaxation as a 0-1 Knapsack problem,
very similar to the \WCRelaxLower relaxation but with a different definition for the relative error,
that is:
\begin{gather*}
\textrm{max.}\quad\sum_{i=0}^{k} f(P_i)x_i,\quad
\textrm{s.t.}\quad\sum_{i=0}^{k} \varepsilon(P_i)x_i \leq M \\
x_i\in\{0,1\}, i\in\{0,\ldots,k\}
\end{gather*}
where $f(P_i)$ is the execution frequency of the instrumented basic block $P_i$, $x_i$ denotes the probes selected for removal, $M$ is the
error threshold, and $\varepsilon(P_i)$ is the error of removing probe $P_i$ relative to the total work.
